---
title: "Salem_visualization_essay"
author: "a guidone"
date: "3/24/2017"
output: html_document
---

```{r}

library(tidyverse)
library(dplyr)
library(lubridate)
library(stringr)
library(forcats)


```

```{r}

salem_crew <- read_csv("salem_crew.csv")
salem_voyages <- read_csv("salem_voyages.csv")

```

3,307 voyages between 1797-1832 and 15,364 sailors(1797-1832 which have full data sets including date, position, and complexion). however, this doesn't account for duplicates. could fix by finding code to possibly combine first and last names into one column and then seeing what the difference in totals is. If insignificant total then probably don't have to worry about it but just note it. 




```{r}

salem_data_joined_birth_year <- salem_crew %>% 
  left_join(salem_voyages, "VoyageId") %>% 
  select(VoyageId, SortDate, BirthPlace) %>%
  na.omit()

extract_year <- function(x) {
  year_char <- stringr::str_extract(x, "\\d{4}") 
  year_int <- as.integer(year_char)
  year_int
}

salem_data_tidy_birth_year <- salem_data_joined_birth_year %>% 
  mutate(SortDate, Year = extract_year(salem_data_joined_birth_year$SortDate)) %>%
  select(-SortDate)

salem_data_tidy_birth_year_1797_1832 <- salem_data_tidy_birth_year %>%
  filter(Year >= 1797, Year <= 1832)
```

```{r}
unique(salem_data_tidy_birth_year_1797_1832$BirthPlace)

```


```{r}

salem_data_tidy_birth_year_1797_1832 %>% 
  count(BirthPlace)

```

```{r}

salem_comprehensive_data <- salem_crew %>% 
  left_join(salem_voyages, "VoyageId")

```


```{r}

salem_data_joined_complexion_year <- salem_comprehensive_data %>% 
  select(VoyageId, SortDate, BirthPlace, Complexion, Position) %>%
  na.omit()
```

```{r}
extract_year <- function(x) {
  year_char <- stringr::str_extract(x, "\\d{4}") 
  year_int <- as.integer(year_char)
  year_int
}
```

```{r}
salem_data_tidy_complexion_year <- salem_data_joined_complexion_year %>% 
  mutate(SortDate, Year = extract_year(salem_data_joined_complexion_year$SortDate)) %>%
  select(-SortDate)
```

```{r}
salem_data_tidy_complexion_year_1797_1832 <- salem_data_tidy_complexion_year %>%
  filter(Year >= 1797, Year <= 1832)
```


```{r}
unique(salem_data_tidy_complexion_year_1797_1832$Complexion)

```

```{r}

complexion_tidy <- data_frame(
  Complexion = c("Dark", "Light", "Black", "Sallow", "Fair", "Ruddy", "Sandy", "Brown", "Yellow","?", "Dark?", "Mulatto", "Florid", "Sambo", "Black (yellow)", "Quadroon", "Pale", "Very Black", "Bright yellow", "Negro", "Fresh", "Lambs?", "Very Dark", "Colored", "Mixed","Very black", "Burnt", "Dark Olive", "Fairish", "Clear/Ruddy", "Fair Ruddy", "Rather Fair", "Clear", "Tawny", "Swarthy", "Light and Fres", "Dark Brown", "Indian", "African", "Black man", "Dark brown", "Light Brown", "Ruddy Brown","Brownish", "Pink?", "Rather Light", "Fairish?"),
  
  Complexion2 = c("Black/Dark", "White/Fair/Ruddy", "Black/Dark", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "Brown/Mulatto", "Yellow/Olive", "Unknown", "Black/Dark", "Brown/Mulatto", "White/Fair/Ruddy", "Black/Dark", "Black/Dark", "Brown/Mulatto", "White/Fair/Ruddy", "Black/Dark", "White/Fair/Ruddy", "Black/Dark", "White/Fair/Ruddy", "Unknown", "Black/Dark", "Black/Dark", "Brown/Mulatto", "Black/Dark", "White/Fair/Ruddy", "Yellow/Olive", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "Brown/Mulatto", "Yellow/Olive", "White/Fair/Ruddy", "Black/Dark", "Indian", "Black/Dark", "Black/Dark", "Black/Dark", "Brown/Mulatto", "Brown/Mulatto", "Brown/Mulatto", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy")
)
```

```{r}
salem_data_tidy_complexion2_year_1797_1832 <- salem_data_tidy_complexion_year_1797_1832 %>%
  left_join(complexion_tidy, by = "Complexion")
```

```{r}

position_tidy <- data_frame(
  Position = c("1st Officer", 
"2nd Officer", 
"Seaman", 
"Steward & Cook", 
"Master", 
"2nd Mate", 
"Cook", 
"First Officer", 
"Clerk", 
"First Mate", 
"Second Mate", 
"Carpenter", 
"?", 
"Steward",
"Mate",
"Second Officer", 
"Orderly, Seaman", 
"Third Mate", 
"Boat Steerer", 
"Ship Keeper", 
"Steward & Seaman", 
"Seaman, Sailmaker", 
"Light Seaman", 
"Orderly?,Seaman",
"Boy", 
"Orderly/Seaman", 
"cook", 
"mate", 
"Carpenter, Seaman", 
"Light? Seamna", 
"2nd officer", 
"Third Officer",
"Harpoonsman", 
"Cooper", 
"Carpenter & Seaman", 
"1st officer", 
"2d officer",
"1st mate", 
"2d mate",   
"1st Mate",
"2d Mate",
"Seaman & Carpenter", 
"carpenter & seaman", 
"Ody?/Light Seaman", 
"1 mate", 
"2 mate", 
"Ordindary Seaman",
"1st", 
"2d",
"first officer", 
"second officer", 
"Clerk Seaman", 
"Cook & Steward", 
"3d mate",                
"Seamen", 
"First officer",          
"Carpenter/Seaman", 
"2d Officer", 
"Mate 1st",
"Mate 2d", 
"2 Mate",
"Ordinary seaman",
"Light seaman",
"Master?",               
"Sec mate", 
"secd Mate", 
"1st Off", 
"2d Off", 
"Secd Mate", 
"Cabin Boy", 
"2nd mate", 
"Third mate/Clerk", 
"Armoure & Seaman", 
"Hand", 
"2nd Mate (crossed out)",
"St. Seaman",
"Officer", 
"Boatswain", 
"Ordinary",
"Supercargo", 
"Captain",
"Seaman and clerk",       
"1sr Mate",
"Stewards or Cook's Mate",
"Passenger",
"First mate", 
"Cabin boy", 
"`",
"Seaman and Cook", 
"Lt Seaman", 
"Second mate", 
"Gunner", 
"Clerk and seaman", 
"Seaman?", 
"Passenger?", 
"Seaman and Carpenter", 
"Carpenter and seaman", 
"Ord Seaman", 
"Captain's ?",
"Secont Mate", 
"3rd Mate", 
"Carpenter and Seaman", 
"Sailor", 
"Super Cargo", 
"Purser", 
"Beverly", 
"Assistant",
"Apprentice",
"Young Seaman",
"Fresh Hand",
"Cook/Boy",
"Assistant [?]", 
"Chief Mate", 
"Clerk and Assistant", 
"Norfolk",
"Clerk/Seaman", 
"Ordinary Seaman",
"Gunner[?]", 
"Fifer[?]",
"Greenhand",
"Ordinary[?]",
"Drummer", 
"Mate\nMate", 
"Cabinh Boy", 
"Mariner", 
"Second Mate`", 
"Seaman/Cooper",
"Steward/Apprentice", 
"Captain's Clerk",
"Seaman/Cook", 
"Chf. Mate", 
"Seaman/Carpenter", 
"Sailmaker", 
"Seaman\nSeaman", 
"Joint Supercargo, w/Cap", 
"Pilot", 
"Supercargo and Passenge", 
"Sail Maker", 
"Cok", 
"Second Mateq", 
"Boy/Cook", 
"Carp[enter", 
"Apprentice.", 
"First Officer[?]", 
"Third Mate/Clerk", 
"Fisrt Officer", 
"Rank", 
"Sail Ward", 
"Stweard", 
"Ist Mate", 
"Assistant[?]", 
"Servant", 
"ond mate", 
"? Mate", 
"Boston", 
"Mate?", 
"Assistance", 
"Third mate", 
"3rd officer", 
"Apprentice and Cook", 
"Greenhand & Carpenter", 
"Assistant & clerk", 
"3rd mate", 
"Carpenter & seaman", 
"Super cargo", 
"Cook & boy",           
"Not given.", 
"Apprentice to Captain", 
"Sailing Master", 
"Super cargo or consigne", 
"Apprentice and Boy", 
"1st mate?", 
"Green hand", 
"Sail-maker", 
"Joint supercargo", 
"Captain assistand", 
"Factor", 
"Apprentice seaman", 
"Steward[?]", 
"Seaman/Boy", 
"1 officer",
"2 officer",
"Ordinary? Seaman", 
"Seaman & carpenter", 
"Chief mate", 
"Cool", 
"Stacker",
"Seaman-Cook",
"Seaman and Cooper",
"Seaman/Steward",
"Steward?", 
"Cook?", 
"Super cargp", 
"1st maste", 
"Seaman Ordy",
"Ordinary seamab",
"1sr mate",
"Seamna",
"Duxbury",
"Cabin passenger", 
"Ordinary, Seaman", 
"Cooper and Seaman", 
"Supercargo[?]",
"3rd Mate/Clerk"),

Position2 = c("Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Cook/Steward",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Unknown",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Navigation",
"Craftsman",
"Cook/Steward",
"Craftsman",
"Seaman",
"Servant/Assistant/Apprentice",
"Cabin Boy",
"Servant/Assistant/Apprentice",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Craftsman",
"Craftsman",
"Craftsman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Craftsman",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Craftsman",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Armorer/Gunner",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Supercargo",
"Captain/Master",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Passenger",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Unknown",
"Cook/Steward",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Armorer/Gunner",
"Clerk",
"Seaman",
"Passenger",
"Craftsman",
"Craftsman",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Seaman",
"Supercargo",
"Clerk",
"Unknown",
"Servant/Assistant/Apprentice",
"Servant/Assistant/Apprentice",
"Seaman",
"Seaman",
"Cook/Steward",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Clerk",
"Unknown",
"Clerk",
"Seaman",
"Armorer/Gunner",
"Fifer/Drummer",
"Seaman",
"Seaman",
"Fifer/Drummer",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Servant/Assistant/Apprentice",
"Clerk",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Craftsman",
"Seaman",
"Captain/Master",
"Navigation",
"Supercargo",
"Craftsman",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Craftsman",
"Servant/Assistant/Apprentice",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Craftsman",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant/Apprentice",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Unknown",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Cook/Steward",
"Craftsman",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Supercargo",
"Cook/Steward",
"Unknown",
"Servant/Assistant/Apprentice",
"Navigation",
"Supercargo",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Craftsman",
"Supercargo",
"Servant/Assistant/Apprentice",
"Clerk",
"Servant/Assistant/Apprentice",
"Cook/Steward",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Craftsman",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Seaman",
"Cook/Steward",
"Craftsman",
"Cook/Steward",
"Cook/Steward",
"Cook/Steward",
"Supercargo",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Unknown",
"Passenger",
"Seaman",
"Craftsman",
"Supercargo",
"Mate (1st, 2nd, 3rd)"))

```


```{r}
salem_data_tidy_complexion2_position2_year_1797_1832 <- salem_data_tidy_complexion2_year_1797_1832 %>% 
  left_join(position_tidy, by = "Position") 
```

```{r}
salem_data_tidy_complexion2_position2_year_1797_1832
```

```{r}
salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 == "Yellow/Olive") 
```


```{r}
salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 == "Black/Dark" | Complexion2 == "White/Fair/Ruddy") %>% 
ggplot(aes(x = Position2, fill = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Sailors Departing Salem, 1797-1832", x = "Occupation", y = "Total")
```

It is commonly known that many African-Americans in the early republic found employment as sailors. However, less studied are individuals from around the world who also found employment at sea. Salem's role as a center of global trade facilitated the appeareance of people from around the world at its docks. These sailors had a complexion classified as "brown", "yellow," "olive" or "Indian" and are present a far more diverse wharf than simply black and white variance.

```{r}

salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 == "Brown/Mulatto" | Complexion2 == "Indian" | Complexion2 == "Yellow/Olive") %>% 
ggplot(aes(x = Position2, fill = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Sailors Departing Salem, 1797-1832", x = "Occupation", y = "Total")

```
shows a lot of yellow/olive were cooks, how did that compare with other races?

```{r}
salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Position2 == "Cook/Steward") %>% 
ggplot(aes(x = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Salem Ship Cooks/Stewards by Race, 1797-1832", x = "Occupation", y = "Total")

```
Using more specific data set (seperates between cooks and stewards)

```{r}
Position3 <- data_frame(
  
  Position = c("1st Officer", 
"2nd Officer", 
"Seaman", 
"Steward & Cook", 
"Master", 
"2nd Mate", 
"Cook", 
"First Officer", 
"Clerk", 
"First Mate", 
"Second Mate", 
"Carpenter", 
"?", 
"Steward",
"Mate",
"Second Officer", 
"Orderly, Seaman", 
"Third Mate", 
"Boat Steerer", 
"Ship Keeper", 
"Steward & Seaman", 
"Seaman, Sailmaker", 
"Light Seaman", 
"Orderly?,Seaman",
"Boy", 
"Orderly/Seaman", 
"cook", 
"mate", 
"Carpenter, Seaman", 
"Light? Seamna", 
"2nd officer", 
"Third Officer",
"Harpoonsman", 
"Cooper", 
"Carpenter & Seaman", 
"1st officer", 
"2d officer",
"1st mate", 
"2d mate",   
"1st Mate",
"2d Mate",
"Seaman & Carpenter", 
"carpenter & seaman", 
"Ody?/Light Seaman", 
"1 mate", 
"2 mate", 
"Ordindary Seaman",
"1st", 
"2d",
"first officer", 
"second officer", 
"Clerk Seaman", 
"Cook & Steward", 
"3d mate",                
"Seamen", 
"First officer",          
"Carpenter/Seaman", 
"2d Officer", 
"Mate 1st",
"Mate 2d", 
"2 Mate",
"Ordinary seaman",
"Light seaman",
"Master?",               
"Sec mate", 
"secd Mate", 
"1st Off", 
"2d Off", 
"Secd Mate", 
"Cabin Boy", 
"2nd mate", 
"Third mate/Clerk", 
"Armoure & Seaman", 
"Hand", 
"2nd Mate (crossed out)",
"St. Seaman",
"Officer", 
"Boatswain", 
"Ordinary",
"Supercargo", 
"Captain",
"Seaman and clerk",       
"1sr Mate",
"Stewards or Cook's Mate",
"Passenger",
"First mate", 
"Cabin boy", 
"`",
"Seaman and Cook", 
"Lt Seaman", 
"Second mate", 
"Gunner", 
"Clerk and seaman", 
"Seaman?", 
"Passenger?", 
"Seaman and Carpenter", 
"Carpenter and seaman", 
"Ord Seaman", 
"Captain's ?",
"Secont Mate", 
"3rd Mate", 
"Carpenter and Seaman", 
"Sailor", 
"Super Cargo", 
"Purser", 
"Beverly", 
"Assistant",
"Apprentice",
"Young Seaman",
"Fresh Hand",
"Cook/Boy",
"Assistant [?]", 
"Chief Mate", 
"Clerk and Assistant", 
"Norfolk",
"Clerk/Seaman", 
"Ordinary Seaman",
"Gunner[?]", 
"Fifer[?]",
"Greenhand",
"Ordinary[?]",
"Drummer", 
"Mate\nMate", 
"Cabinh Boy", 
"Mariner", 
"Second Mate`", 
"Seaman/Cooper",
"Steward/Apprentice", 
"Captain's Clerk",
"Seaman/Cook", 
"Chf. Mate", 
"Seaman/Carpenter", 
"Sailmaker", 
"Seaman\nSeaman", 
"Joint Supercargo, w/Cap", 
"Pilot", 
"Supercargo and Passenge", 
"Sail Maker", 
"Cok", 
"Second Mateq", 
"Boy/Cook", 
"Carp[enter", 
"Apprentice.", 
"First Officer[?]", 
"Third Mate/Clerk", 
"Fisrt Officer", 
"Rank", 
"Sail Ward", 
"Stweard", 
"Ist Mate", 
"Assistant[?]", 
"Servant", 
"ond mate", 
"? Mate", 
"Boston", 
"Mate?", 
"Assistance", 
"Third mate", 
"3rd officer", 
"Apprentice and Cook", 
"Greenhand & Carpenter", 
"Assistant & clerk", 
"3rd mate", 
"Carpenter & seaman", 
"Super cargo", 
"Cook & boy",           
"Not given.", 
"Apprentice to Captain", 
"Sailing Master", 
"Super cargo or consigne", 
"Apprentice and Boy", 
"1st mate?", 
"Green hand", 
"Sail-maker", 
"Joint supercargo", 
"Captain assistand", 
"Factor", 
"Apprentice seaman", 
"Steward[?]", 
"Seaman/Boy", 
"1 officer",
"2 officer",
"Ordinary? Seaman", 
"Seaman & carpenter", 
"Chief mate", 
"Cool", 
"Stacker",
"Seaman-Cook",
"Seaman and Cooper",
"Seaman/Steward",
"Steward?", 
"Cook?", 
"Super cargp", 
"1st maste", 
"Seaman Ordy",
"Ordinary seamab",
"1sr mate",
"Seamna",
"Duxbury",
"Cabin passenger", 
"Ordinary, Seaman", 
"Cooper and Seaman", 
"Supercargo[?]",
"3rd Mate/Clerk"),

Position3 = c("Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Cook",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Cook",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Unknown",
"Steward",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Orderly",
"Mate (1st, 2nd, 3rd)",
"Pilot/Steerer",
"Ship Keeper",
"Steward",
"Sailmaker",
"Seaman",
"Orderly",
"Cabin Boy",
"Orderly",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Harpoonsman",
"Cooper",
"Carpenter",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Carpenter",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Carpenter",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Armorer",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Boatswain",
"Seaman",
"Supercargo",
"Captain/Master",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Steward",
"Passenger",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Unknown",
"Cook",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Gunner",
"Clerk",
"Seaman",
"Passenger",
"Carpenter",
"Carpenter",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Seaman",
"Supercargo",
"Purser",
"Unknown",
"Servant/Assistant",
"Apprentice",
"Seaman",
"Seaman",
"Cook",
"Servant/Assistant",
"Mate (1st, 2nd, 3rd)",
"Clerk",
"Unknown",
"Clerk",
"Seaman",
"Gunner",
"Fifer",
"Seaman",
"Seaman",
"Drummer",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Cooper",
"Apprentice",
"Clerk",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Sailmaker",
"Seaman",
"Captain/Master",
"Pilot/Steerer",
"Supercargo",
"Sailmaker",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Cook",
"Carpenter",
"Apprentice",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Sail Ward",
"Steward",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant",
"Servant/Assistant",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Unknown",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Cook",
"Carpenter",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Supercargo",
"Cook",
"Unknown",
"Apprentice",
"Sailing Master",
"Supercargo",
"Apprentice",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Sailmaker",
"Supercargo",
"Servant/Assistant",
"Factor",
"Apprentice",
"Steward",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Carpenter",
"Mate (1st, 2nd, 3rd)",
"Cook",
"Seaman",
"Cook",
"Cooper",
"Steward",
"Steward",
"Cook",
"Supercargo",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Unknown",
"Passenger",
"Seaman",
"Cooper",
"Supercargo",
"Mate (1st, 2nd, 3rd)"))


```

```{r}

salem_data_tidy_complexion2_position3_year_1797_1832 <- salem_data_tidy_complexion2_year_1797_1832 %>% 
  left_join(Position3, by = "Position")
```

```{r}
salem_data_tidy_complexion2_position3_year_1797_1832 %>% 
  filter(Position3 == "Cook") %>% 
ggplot(aes(x = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Ship Cooks Departing Salem, 1797-1832", x = "Complexion", y = "Total")

```
Let's learn more about the Brown/Mulatto, Indian, and Olive/Yellow sailors.


```{r}
salem_data_tidy_complexion2_position3_year_1797_1832 %>%
  filter(Complexion2 == "Brown/Mulatto" | Complexion2 == "Indian" | Complexion2 == "Yellow/Olive") %>% 
  ggplot(aes(x = Position3, fill = Complexion2)) + geom_bar() + coord_flip()
```

```{r}

salem_data_world_connections_year_1797_1832 <- salem_data_tidy_complexion2_position3_year_1797_1832 %>% 
  filter(Complexion2 == "Brown/Mulatto" | Complexion2 == "Indian" | Complexion2 == "Yellow/Olive")
```

442 entries (some could be doubles). George Emerson, the cook born in Topsfield is one. Travels 4 times. Abandoned ship in Salem for a year before taking sailing again, always worked as a cook. 




```{r}

BirthPlace2 <- data_frame(
  BirthPlace = c("Manchester",
"Maryland",
"Portsmouth, NH?",
"Java?",
"Petersbury",
"Delaware",
"Ipswich",
"Portsmouth",
"Baltimore",
"Boston",
"New York",
"Philadelphia",
"Germantown",
"Orleans, Cape Cod",
"Stockholm",
"Africa",
"Nantucket",
"New Orleans",
"Salem",
"Bridgeport",
"Canton",
"USA",
"Alexandria",
"Georgetown",
"Marblehead",
"Newton, NJ",
"Bath",
"North Kingston",
"Dunbarton, NH",
"Mississippi",
"Providence, R.I.",
"Rhode Island",
"Gloucester",
"Portland",
"Norwalk",
"Island of Tucina?",
"Newton",
"Kemacton?",
"Hingham",
"Beverly",
"Charleston",
"Kington, Pennsylvania",
"Gottenburg?",
"Albany",
"Massachusetts",
"Hampshire",
"Danzig",
"Norfolk",
"Danvers",
"England",
"Newport, RI",
"New Bern, NC",
"Lime Lyme?",
"St. Martin",
"South Carolina",
"Andover",
"New Jersey",
"Newark, (NJ)",
"Calcutta",
"?",
"Portugal",
"Helsingford",
"Altona",
"Newport, (RI)",
"Bengal",
"Wallingford",
"Worcester",
"Charles County",
"China",
"Sardinia",
"St. Iago",
"Cattaro",
"Prince George Virginia",
"Williamstown",
"Buck's County",
"St. Domingo",
"Oporto",
"Wilmington",
"Hide County, N.L.?",
"Norway",
"Island of Magdaline",
"Granby",
"New Bedford",
"Annapolis",
"Charles County, MD",
"Edenton",
"Cape Verde",
"Rio Janeiro",
"India",
"Newburyport",
"Hopkinton",
"Copenhagen",
"Virginia",
"Bucks County, PA",
"S. America",
"Litchfield, CT",
"Madeira",
"Sweden",
"Helsinburgh",
"Savannah",
"Montgomery",
"Gottenburg",
"Beaufort, SC",
"Kent?",
"Mt. Desert",
"Camden",
"Peru, NY",
"Stetten",
"Charlestown",
"Deer Isle",
"Stettin",
"Narragansett, RI",
"Mawee",
"Connecticut",
"North Bergen",
"Richmond",
"Rio de Janeiro",
"Richmond, VA",
"Southwark?",
"Bucks County",
"Manilla",
"Dram, Norway",
"Newport",
"Holstein",
"Pennsylvania",
"Georgetown, MD",
"Charlestown, SC",
"Albany, NY",
"Essex County",
"Somersett Conty",
"Topsfield",
"Trieste",
"Elson fort",
"Westchester Co.",
"Newark, N. J.",
"Leghorn",
"Little York",
"Falmar, Sweden",
"Long Island",
"East India",
"Kennebrook",
"Martha Vine Yard",
"Norfolk Va",
"Somerset",
"Accomack",
"Isle of Magdalena",
"Fells Point, MD",
"Calmar",
"Berwick",
"Topsieild",
"State of New York",
"Marthas Vinyard",
"Cumberland County, NJ",
"Cumberland",
"Middleton",
"Southampton",
"Italy",
"Posquotark",
"NewBern",
"Hamburg",
"Masschusetts",
"Duxbury",
"Snowhill",
"Wiscasset",
"East Indies",
"Sumatra"),

City = c("Manchester",
"NA",
"Portsmouth",
"NA",
"Petersburg",
"NA",
"Ipswich",
"Portsmouth",
"Baltimore",
"Boston",
"New York",
"Philadelphia",
"Germantown",
"Orleans, Cape Cod",
"Stockholm",
"NA",
"Nantucket",
"New Orleans",
"Salem",
"Bridgeport",
"Canton",
"NA",
"Alexandria",
"Georgetown",
"Marblehead",
"Newtown",
"Bath",
"Kingston",
"Dunbarton",
"NA",
"Providence",
"NA",
"Gloucester",
"Portland",
"Norwalk",
"NA",
"Newton",
"Thomaston",
"Hingham",
"Beverly",
"Charleston",
"Kingston",
"Gothenburg",
"Albany",
"NA",
"Hampshire",
"Danzig",
"Norfolk",
"Danvers",
"NA",
"Newport",
"New Bern",
"Lyme",
"NA",
"NA",
"Andover",
"NA",
"Newark",
"Calcutta",
"NA",
"NA",
"Helsinki",
"Altona",
"Newport",
"Bengal",
"Wallingford",
"Worcester",
"Charles County",
"NA",
"NA",
"St. Iago",
"Kotor",
"Prince George",
"Williamstown",
"Buck's County",
"NA",
"Porto",
"Wilmington",
"Hide County",
"NA",
"Maddalena",
"Granby",
"New Bedford",
"Annapolis",
"Charles County",
"Edenton",
"NA",
"Rio de Janeiro",
"NA",
"Newburyport",
"Hopkinton",
"Copenhagen",
"NA",
"Buck's County",
"NA",
"Litchfield",
"NA",
"NA",
"Helsinki",
"Savannah",
"Montgomery",
"Gothenburg",
"Beaufort",
"Kent County",
"Mt. Desert",
"Camden",
"Peru",
"Stetten",
"Charlestown",
"Deer Isle",
"Szczecin",
"Narragansett",
"NA",
"NA",
"North Bergen",
"Richmond",
"Rio de Janeiro",
"Richmond",
"Southwick",
"Buck's County",
"Manila",
"Dram",
"Newport",
"Holstein",
"NA",
"Georgetown",
"Charleston",
"Albany",
"Essex County",
"Somerset County",
"Topsfield",
"Trieste",
"Elson Fort",
"Westchester",
"Newark",
"Livorno",
"Little York",
"Falmar",
"Long Island",
"East India",
"Kennebunk",
"Martha's Vineyard",
"Norfolk",
"Somerset County",
"Accomack",
"Maddalena",
"Fells Point",
"Kalmar",
"Berwick",
"Topsfield",
"NA",
"Martha's Vineyard",
"Cumberland County",
"Cumberland",
"Middleton",
"Southampton",
"NA",
"Pasquotank",
"New Bern",
"Hamburg",
"NA",
"Duxbury",
"Snowhill",
"Wiscasset",
"NA",
"NA"),

State = c("Massachusetts",
"Maryland",
"New Hampshire",
"NA",
"Virginia",
"Delaware",
"Massachusetts",
"New Hampshire",
"Maryland",
"Massachusetts",
"New York",
"Pennsylvania",
"Maryland",
"Massachusetts",
"NA",
"NA",
"Massachusetts",
"Louisiana", 
"Massachusetts",
"Connecticut",
"NA",
"NA",
"Virginia",
"Maryland",
"Massachusetts",
"New Jersey",
"Maine",
"NA",
"New Hampshire",
"Mississippi",
"Rhode Island",
"Rhode Island",
"Massachusetts",
"Maine",
"Connecticut",
"NA",
"Massachusetts",
"Connecticut",
"Massachusetts",
"Massachusetts",
"South Carolina",
"Pennsylvania",
"NA",
"New York",
"Massachusetts",
"Massachusetts",
"NA",
"Virginia",
"Massachusetts",
"NA",
"Rhode Island",
"North Carolina",
"Connecticut",
"NA",
"South Carolina",
"Massachusetts",
"New Jersey",
"New Jersey",
"NA",
"NA",
"NA",
"NA",
"NA",
"Rhode Island",
"NA",
"Connecticut",
"Massachusetts",
"Maryland",
"NA",
"NA",
"NA",
"NA",
"Virginia",
"Massachusetts",
"Pennsylvania",
"NA",
"NA",
"Delaware",
"North Carolina",
"NA",
"NA",
"Connecticut",
"Massachusetts",
"Maryland",
"Maryland",
"North Carolina",
"NA",
"NA",
"NA",
"Massachusetts",
"Massachusetts",
"NA",
"Virginia",
"Pennsylvania",
"NA",
"Connecticut",
"NA",
"NA",
"NA",
"Georgia",
"Alabama",
"NA",
"South Carolina",
"Maryland",
"Maine",
"New Jersey",
"New York",
"NA",
"Massachusetts",
"Maine",
"NA",
"Rhode Island",
"NA",
"Connecticut",
"New Jersey",
"Virginia",
"NA",
"Virginia",
"Massachusetts",
"Pennsylvania",
"NA",
"NA",
"Rhode Island",
"NA",
"Pennsylvania",
"Maryland",
"South Carolina",
"New York",
"Massachusetts",
"Maryland",
"Massachusetts",
"NA",
"NA",
"New York",
"New Jersey",
"NA",
"Pennsylvania",
"NA",
"New York",
"NA",
"Maine",
"Massachusetts",
"Virginia",
"Maryland",
"Virginia",
"NA",
"Maryland",
"NA",
"Pennsylvania",
"Massachusetts",
"New York",
"Massachusetts",
"New Jersey",
"Maryland",
"Massachusetts",
"Massachusetts",
"NA",
"North Carolina",
"North Carolina",
"NA",
"Massachusetts",
"Massachusetts",
"Maryland",
"Maine",
"NA",
"NA"),

Country = c("USA",
"USA",
"USA",
"Java",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Sweden",
"Africa",
"USA",
"USA",
"USA",
"USA",
"China",
"NA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Jamaica",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Island of Terceira",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Sweden",
"USA",
"USA",
"USA",
"Prussia",
"USA",
"USA",
"England",
"USA",
"USA",
"USA",
"St. Martin",
"USA",
"USA",
"USA",
"USA",
"India",
"NA",
"Portugal",
"Sweden",
"Denmark",
"USA",
"India",
"USA",
"USA",
"USA",
"China",
"Sardinia",
"Cuba",
"Montenegro",
"USA",
"USA",
"USA",
"St. Domingo",
"Portugal",
"USA",
"USA",
"Norway",
"Sardinia",
"USA",
"USA",
"USA",
"USA",
"USA",
"Cape Verde",
"Brazil",
"India",
"USA",
"USA",
"Denmark",
"USA",
"USA",
"NA",
"USA",
"Madeira",
"Sweden",
"Sweden",
"USA",
"USA",
"Sweden",
"USA",
"USA",
"USA",
"USA",
"USA",
"Prussia",
"USA",
"USA",
"Prussia",
"USA",
"Maui",
"USA",
"USA",
"USA",
"Brazil",
"USA",
"USA",
"USA",
"Philippines",
"Norway",
"USA",
"Denmark",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Italy",
"Sweden",
"USA",
"USA",
"Italy",
"USA",
"Sweden",
"USA",
"India",
"USA",
"USA",
"USA",
"USA",
"USA",
"Sardinia",
"USA",
"Sweden",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Italy",
"USA",
"USA",
"Germany",
"USA",
"USA",
"USA",
"USA",
"East Indies",
"Sumatra"),

Region = c("North America",
"North America",
"North America",
"East Indies",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Scandanavia",
"Africa",
"North America",
"North America",
"North America",
"North America",
"North America",
"NA",
"North America",
"North America",
"North America",
"North America",
"North America",
"Caribbean",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Atlantic Islands",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Scandanavia",
"North America",
"North America",
"North America",
"Europe",
"North America",
"North America",
"Europe",
"North America",
"North America",
"North America",
"Caribbean",
"North America",
"North America",
"North America",
"North America",
"India",
"NA",
"Europe",
"Scandanavia",
"Europe",
"North America",
"India",
"North America",
"North America",
"North America",
"Asia",
"Europe",
"Caribbean",
"Europe",
"North America",
"North America",
"North America",
"Caribbean",
"Europe",
"North America",
"North America",
"Scandanavia",
"Europe",
"North America",
"North America",
"North America",
"North America",
"North America",
"Africa",
"South America",
"India",
"North America",
"North America",
"Europe",
"North America",
"North America",
"South America",
"North America",
"Atlantic Islands",
"Scandanavia",
"Scandanavia",
"North America",
"North America",
"Scandanavia",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"North America",
"North America",
"Europe",
"North America",
"Pacific Islands",
"North America",
"North America",
"North America",
"South America",
"North America",
"North America",
"North America",
"Asia",
"Scandanavia",
"North America",
"Europe",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"Scandanavia",
"North America",
"North America",
"Europe",
"North America",
"Scandanavia",
"North America",
"India",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"North America",
"Scandanavia",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"India",
"India"))
```

```{r}
salem_data_world_connections_BirthPlace2_year_1797_1832 <- salem_data_world_connections_year_1797_1832 %>% 
  left_join(BirthPlace2, by = "BirthPlace")
```



```{r}

salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Region != "North America", Country != "NA") %>% 
  ggplot(aes(x = Position3, fill = Region, na.rm = TRUE))+
  geom_bar() + coord_flip()
```

```{r}
salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Region == "Atlantic Islands") %>% 
  ggplot(aes(x = Country))+
  geom_bar() + coord_flip()

```

```{r}

salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Position2 != "Unknown") %>% 
  ggplot(aes(x = Position2)) + geom_bar() + facet_wrap(~ Complexion2, scales = "free_x") +coord_flip() + labs(title = "Sailors of Color, 1797-1832", x = "Position", y = "Total", caption = "This graph counts represents the occupation of each sailor every time they appeared on a crew list. Thus, if a sailor took two voyages they would be recorded twice. However, whether or not a 'yellow/olive' cook was a different person or the same individual on 3 seperate voyages matters less than the fact that there was a 'yellow/olive' cook on three seperate voyages.")
```

