---
title: "Salem's Global Sailors: Visualization Essay"
author: "a guidone"
date: "3/27/2017"
output: html_document
---

```{r, echo = FALSE, include=FALSE}

library(tidyverse)
library(dplyr)
library(lubridate)
library(stringr)
library(forcats)

```

```{r, echo = FALSE, include=FALSE}
salem_crew <- read_csv("salem_crew_original.csv")
salem_voyages <- read_csv("salem_voyages_original.csv")
```

```{r, echo = FALSE, include=FALSE}

salem_data_joined_birth_year <- salem_crew %>% 
  left_join(salem_voyages, "VoyageId") %>% 
  select(VoyageId, SortDate, BirthPlace) %>%
  na.omit()

extract_year <- function(x) {
  year_char <- stringr::str_extract(x, "\\d{4}") 
  year_int <- as.integer(year_char)
  year_int
}

salem_data_tidy_birth_year <- salem_data_joined_birth_year %>% 
  mutate(SortDate, Year = extract_year(salem_data_joined_birth_year$SortDate)) %>%
  select(-SortDate)

salem_data_tidy_birth_year_1797_1832 <- salem_data_tidy_birth_year %>%
  filter(Year >= 1797, Year <= 1832)
```

```{r, echo = FALSE, include=FALSE}

salem_comprehensive_data <- salem_crew %>% 
  left_join(salem_voyages, "VoyageId")
```

```{r, echo = FALSE, include=FALSE}
salem_data_joined_complexion_year <- salem_comprehensive_data %>% 
  select(VoyageId, SortDate, BirthPlace, Complexion, Position) %>%
  na.omit()
```

```{r, echo = FALSE, include=FALSE}

extract_year <- function(x) {
  year_char <- stringr::str_extract(x, "\\d{4}") 
  year_int <- as.integer(year_char)
  year_int
}
```

```{r, echo = FALSE, include=FALSE}

salem_data_tidy_complexion_year <- salem_data_joined_complexion_year %>% 
  mutate(SortDate, Year = extract_year(salem_data_joined_complexion_year$SortDate)) %>%
  select(-SortDate)
```

```{r, echo = FALSE, include=FALSE}

salem_data_tidy_complexion_year_1797_1832 <- salem_data_tidy_complexion_year %>%
  filter(Year >= 1797, Year <= 1832)

```

```{r, echo = FALSE, include=FALSE}

complexion_tidy <- data_frame(
  Complexion = c("Dark", "Light", "Black", "Sallow", "Fair", "Ruddy", "Sandy", "Brown", "Yellow","?", "Dark?", "Mulatto", "Florid", "Sambo", "Black (yellow)", "Quadroon", "Pale", "Very Black", "Bright yellow", "Negro", "Fresh", "Lambs?", "Very Dark", "Colored", "Mixed","Very black", "Burnt", "Dark Olive", "Fairish", "Clear/Ruddy", "Fair Ruddy", "Rather Fair", "Clear", "Tawny", "Swarthy", "Light and Fres", "Dark Brown", "Indian", "African", "Black man", "Dark brown", "Light Brown", "Ruddy Brown","Brownish", "Pink?", "Rather Light", "Fairish?"),
  
  Complexion2 = c("Black/Dark", "White/Fair/Ruddy", "Black/Dark", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "Brown/Mulatto", "Yellow/Olive", "Unknown", "Black/Dark", "Brown/Mulatto", "White/Fair/Ruddy", "Black/Dark", "Black/Dark", "Brown/Mulatto", "White/Fair/Ruddy", "Black/Dark", "White/Fair/Ruddy", "Black/Dark", "White/Fair/Ruddy", "Unknown", "Black/Dark", "Black/Dark", "Brown/Mulatto", "Black/Dark", "White/Fair/Ruddy", "Yellow/Olive", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy", "Brown/Mulatto", "Yellow/Olive", "White/Fair/Ruddy", "Black/Dark", "Indian", "Black/Dark", "Black/Dark", "Black/Dark", "Brown/Mulatto", "Brown/Mulatto", "Brown/Mulatto", "White/Fair/Ruddy", "White/Fair/Ruddy", "White/Fair/Ruddy")
)
```

```{r, echo = FALSE, include=FALSE}
salem_data_tidy_complexion2_year_1797_1832 <- salem_data_tidy_complexion_year_1797_1832 %>%
  left_join(complexion_tidy, by = "Complexion")
```


```{r}

salem_black <- salem_data_tidy_complexion2_year_1797_1832 %>% 
  filter(Complexion2 == "Black/Dark")

unique(salem_black$BirthPlace)
```




```{r, echo = FALSE, include=FALSE}
position_tidy <- data_frame(
  Position = c("1st Officer", 
"2nd Officer", 
"Seaman", 
"Steward & Cook", 
"Master", 
"2nd Mate", 
"Cook", 
"First Officer", 
"Clerk", 
"First Mate", 
"Second Mate", 
"Carpenter", 
"?", 
"Steward",
"Mate",
"Second Officer", 
"Orderly, Seaman", 
"Third Mate", 
"Boat Steerer", 
"Ship Keeper", 
"Steward & Seaman", 
"Seaman, Sailmaker", 
"Light Seaman", 
"Orderly?,Seaman",
"Boy", 
"Orderly/Seaman", 
"cook", 
"mate", 
"Carpenter, Seaman", 
"Light? Seamna", 
"2nd officer", 
"Third Officer",
"Harpoonsman", 
"Cooper", 
"Carpenter & Seaman", 
"1st officer", 
"2d officer",
"1st mate", 
"2d mate",   
"1st Mate",
"2d Mate",
"Seaman & Carpenter", 
"carpenter & seaman", 
"Ody?/Light Seaman", 
"1 mate", 
"2 mate", 
"Ordindary Seaman",
"1st", 
"2d",
"first officer", 
"second officer", 
"Clerk Seaman", 
"Cook & Steward", 
"3d mate",                
"Seamen", 
"First officer",          
"Carpenter/Seaman", 
"2d Officer", 
"Mate 1st",
"Mate 2d", 
"2 Mate",
"Ordinary seaman",
"Light seaman",
"Master?",               
"Sec mate", 
"secd Mate", 
"1st Off", 
"2d Off", 
"Secd Mate", 
"Cabin Boy", 
"2nd mate", 
"Third mate/Clerk", 
"Armoure & Seaman", 
"Hand", 
"2nd Mate (crossed out)",
"St. Seaman",
"Officer", 
"Boatswain", 
"Ordinary",
"Supercargo", 
"Captain",
"Seaman and clerk",       
"1sr Mate",
"Stewards or Cook's Mate",
"Passenger",
"First mate", 
"Cabin boy", 
"`",
"Seaman and Cook", 
"Lt Seaman", 
"Second mate", 
"Gunner", 
"Clerk and seaman", 
"Seaman?", 
"Passenger?", 
"Seaman and Carpenter", 
"Carpenter and seaman", 
"Ord Seaman", 
"Captain's ?",
"Secont Mate", 
"3rd Mate", 
"Carpenter and Seaman", 
"Sailor", 
"Super Cargo", 
"Purser", 
"Beverly", 
"Assistant",
"Apprentice",
"Young Seaman",
"Fresh Hand",
"Cook/Boy",
"Assistant [?]", 
"Chief Mate", 
"Clerk and Assistant", 
"Norfolk",
"Clerk/Seaman", 
"Ordinary Seaman",
"Gunner[?]", 
"Fifer[?]",
"Greenhand",
"Ordinary[?]",
"Drummer", 
"Mate\nMate", 
"Cabinh Boy", 
"Mariner", 
"Second Mate`", 
"Seaman/Cooper",
"Steward/Apprentice", 
"Captain's Clerk",
"Seaman/Cook", 
"Chf. Mate", 
"Seaman/Carpenter", 
"Sailmaker", 
"Seaman\nSeaman", 
"Joint Supercargo, w/Cap", 
"Pilot", 
"Supercargo and Passenge", 
"Sail Maker", 
"Cok", 
"Second Mateq", 
"Boy/Cook", 
"Carp[enter", 
"Apprentice.", 
"First Officer[?]", 
"Third Mate/Clerk", 
"Fisrt Officer", 
"Rank", 
"Sail Ward", 
"Stweard", 
"Ist Mate", 
"Assistant[?]", 
"Servant", 
"ond mate", 
"? Mate", 
"Boston", 
"Mate?", 
"Assistance", 
"Third mate", 
"3rd officer", 
"Apprentice and Cook", 
"Greenhand & Carpenter", 
"Assistant & clerk", 
"3rd mate", 
"Carpenter & seaman", 
"Super cargo", 
"Cook & boy",           
"Not given.", 
"Apprentice to Captain", 
"Sailing Master", 
"Super cargo or consigne", 
"Apprentice and Boy", 
"1st mate?", 
"Green hand", 
"Sail-maker", 
"Joint supercargo", 
"Captain assistand", 
"Factor", 
"Apprentice seaman", 
"Steward[?]", 
"Seaman/Boy", 
"1 officer",
"2 officer",
"Ordinary? Seaman", 
"Seaman & carpenter", 
"Chief mate", 
"Cool", 
"Stacker",
"Seaman-Cook",
"Seaman and Cooper",
"Seaman/Steward",
"Steward?", 
"Cook?", 
"Super cargp", 
"1st maste", 
"Seaman Ordy",
"Ordinary seamab",
"1sr mate",
"Seamna",
"Duxbury",
"Cabin passenger", 
"Ordinary, Seaman", 
"Cooper and Seaman", 
"Supercargo[?]",
"3rd Mate/Clerk"),

Position2 = c("Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Cook/Steward",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Unknown",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Navigation",
"Craftsman",
"Cook/Steward",
"Craftsman",
"Seaman",
"Servant/Assistant/Apprentice",
"Cabin Boy",
"Servant/Assistant/Apprentice",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Craftsman",
"Craftsman",
"Craftsman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Craftsman",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Craftsman",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Armorer/Gunner",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Supercargo",
"Captain/Master",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Passenger",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Unknown",
"Cook/Steward",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Armorer/Gunner",
"Clerk",
"Seaman",
"Passenger",
"Craftsman",
"Craftsman",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Seaman",
"Supercargo",
"Clerk",
"Unknown",
"Servant/Assistant/Apprentice",
"Servant/Assistant/Apprentice",
"Seaman",
"Seaman",
"Cook/Steward",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Clerk",
"Unknown",
"Clerk",
"Seaman",
"Armorer/Gunner",
"Fifer/Drummer",
"Seaman",
"Seaman",
"Fifer/Drummer",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Servant/Assistant/Apprentice",
"Clerk",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Craftsman",
"Seaman",
"Captain/Master",
"Navigation",
"Supercargo",
"Craftsman",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Craftsman",
"Servant/Assistant/Apprentice",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Craftsman",
"Cook/Steward",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant/Apprentice",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Unknown",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Cook/Steward",
"Craftsman",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Craftsman",
"Supercargo",
"Cook/Steward",
"Unknown",
"Servant/Assistant/Apprentice",
"Navigation",
"Supercargo",
"Servant/Assistant/Apprentice",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Craftsman",
"Supercargo",
"Servant/Assistant/Apprentice",
"Clerk",
"Servant/Assistant/Apprentice",
"Cook/Steward",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Craftsman",
"Mate (1st, 2nd, 3rd)",
"Cook/Steward",
"Seaman",
"Cook/Steward",
"Craftsman",
"Cook/Steward",
"Cook/Steward",
"Cook/Steward",
"Supercargo",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Unknown",
"Passenger",
"Seaman",
"Craftsman",
"Supercargo",
"Mate (1st, 2nd, 3rd)"))
```

```{r, echo = FALSE, include=FALSE}
salem_data_tidy_complexion2_position2_year_1797_1832 <- salem_data_tidy_complexion2_year_1797_1832 %>% 
  left_join(position_tidy, by = "Position") 
```

## Introduction: Salem Sailors: 1797-1832

This is an exploration data on sailors departing Salem, Massachusetts from 1797-1832. The data includes 3,307 voyages with 15,364 sailors with complete records. It should be noted that the 15,364 number does not mean that there were 15,364 individuals who were sailors on voyages as duplicates were not removed. This is important to remember but does not detract from the value of this data. For the purposes of this research, whether or not a cook described as 'yellow/olive' was a different person, or the same individual, on 3 different voyages matters less than the fact that there was a 'yellow/olive' cook on three different voyages departing Salem from 1797-1832.


A law passed in 1803 required crew lists to be kept which asked specific questions about each sailor including their birthplace, complexion, and position. It is important to remember that this did not ask for a sailor’s “race” but rather their “complexion.” Entries for “fair” and “ruddy” were common rather than simply “white.” The word “negro” was used at times for black people. Thus, records after 1803 are extremely thorough whereas the 1790s are not included in this dataset (except a few entered for 1797). I have removed all entries which do not meet all criteria examined. If I am looking at sailors’ birthplaces and positions, an entry which recorded a sailor’s birthplace but not his position is discarded. 


Common understandings of early American shipping include the presence of African-Americans and black people onboard ships. The hustle and bustle of a sea port combined with ready access to free states or countries often allowed enslaved black people to reach freedom, such as Frederick Douglass who escaped from Baltimore. The data from Salem supports this understanding.

```{r, echo=FALSE}
salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown") %>% 
ggplot(aes(x = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Fig.1 Sailors Departing Salem, 1797-1832", x = "Complexion", y = "Total")
```

Less recognized is the presence of a group of in-between sailors who did not fit into simple black/white categorizations. Not black or dark, but also not white or fair skinned, these sailors were described as “Yellow,” “Olive,” “Swarthy”, “Indian,” “Brown,” and “Mulatto.” As can be seen above, these individuals were a minority on Salem ships but still warrant closer study for the unique diversity they represented. We will call these “global sailors” and they revealed that Salem’s position as a fulcrum of world trade created more than black/white diversity at the wharf and on ship. We can begin to get a deeper understanding of our global sailors by examining what positions they held at sea.

```{r, echo = FALSE}

salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Position2 != "Unknown") %>% 
  
ggplot(aes(x = Position2, fill = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Fig.2 Roles Aboard Ship, 1797-1832", x = "Position", y = "Total", fill = "Complexion", caption = "Craftsman = Sailmaker, Carpenter, Cooper, Harpoonsman")

```

Most Global Sailors did not rise very high on the ship hierarchy. One of the most popular occupations for Global Sailors was as a cook.


```{r, echo = FALSE}
salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 == "Brown/Mulatto" | Complexion2 == "Indian" | Complexion2 == "Yellow/Olive", Position2 != "Unknown") %>% 
ggplot(aes(x = Position2, fill = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Fig.3 Global Sailors, 1797-1832", x = "Occupation", y = "Total", fill = "Complexion", caption = "Note the high number of 'Yellow/Olive' cooks and stewards")
```
Proportionately Global Sailors were a minority of cooks and stewards, but other than seaman this was the most popular occupation they achieved.
 
```{r, echo = FALSE}

salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Position2 == "Cook/Steward") %>% 
ggplot(aes(x = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Fig.4 Salem Ship Cooks/Stewards by Complexion, 1797-1832", x = "Occupation", y = "Total")

```


```{r, echo = FALSE, include=FALSE}

Position3 <- data_frame(
  
  Position = c("1st Officer", 
"2nd Officer", 
"Seaman", 
"Steward & Cook", 
"Master", 
"2nd Mate", 
"Cook", 
"First Officer", 
"Clerk", 
"First Mate", 
"Second Mate", 
"Carpenter", 
"?", 
"Steward",
"Mate",
"Second Officer", 
"Orderly, Seaman", 
"Third Mate", 
"Boat Steerer", 
"Ship Keeper", 
"Steward & Seaman", 
"Seaman, Sailmaker", 
"Light Seaman", 
"Orderly?,Seaman",
"Boy", 
"Orderly/Seaman", 
"cook", 
"mate", 
"Carpenter, Seaman", 
"Light? Seamna", 
"2nd officer", 
"Third Officer",
"Harpoonsman", 
"Cooper", 
"Carpenter & Seaman", 
"1st officer", 
"2d officer",
"1st mate", 
"2d mate",   
"1st Mate",
"2d Mate",
"Seaman & Carpenter", 
"carpenter & seaman", 
"Ody?/Light Seaman", 
"1 mate", 
"2 mate", 
"Ordindary Seaman",
"1st", 
"2d",
"first officer", 
"second officer", 
"Clerk Seaman", 
"Cook & Steward", 
"3d mate",                
"Seamen", 
"First officer",          
"Carpenter/Seaman", 
"2d Officer", 
"Mate 1st",
"Mate 2d", 
"2 Mate",
"Ordinary seaman",
"Light seaman",
"Master?",               
"Sec mate", 
"secd Mate", 
"1st Off", 
"2d Off", 
"Secd Mate", 
"Cabin Boy", 
"2nd mate", 
"Third mate/Clerk", 
"Armoure & Seaman", 
"Hand", 
"2nd Mate (crossed out)",
"St. Seaman",
"Officer", 
"Boatswain", 
"Ordinary",
"Supercargo", 
"Captain",
"Seaman and clerk",       
"1sr Mate",
"Stewards or Cook's Mate",
"Passenger",
"First mate", 
"Cabin boy", 
"`",
"Seaman and Cook", 
"Lt Seaman", 
"Second mate", 
"Gunner", 
"Clerk and seaman", 
"Seaman?", 
"Passenger?", 
"Seaman and Carpenter", 
"Carpenter and seaman", 
"Ord Seaman", 
"Captain's ?",
"Secont Mate", 
"3rd Mate", 
"Carpenter and Seaman", 
"Sailor", 
"Super Cargo", 
"Purser", 
"Beverly", 
"Assistant",
"Apprentice",
"Young Seaman",
"Fresh Hand",
"Cook/Boy",
"Assistant [?]", 
"Chief Mate", 
"Clerk and Assistant", 
"Norfolk",
"Clerk/Seaman", 
"Ordinary Seaman",
"Gunner[?]", 
"Fifer[?]",
"Greenhand",
"Ordinary[?]",
"Drummer", 
"Mate\nMate", 
"Cabinh Boy", 
"Mariner", 
"Second Mate`", 
"Seaman/Cooper",
"Steward/Apprentice", 
"Captain's Clerk",
"Seaman/Cook", 
"Chf. Mate", 
"Seaman/Carpenter", 
"Sailmaker", 
"Seaman\nSeaman", 
"Joint Supercargo, w/Cap", 
"Pilot", 
"Supercargo and Passenge", 
"Sail Maker", 
"Cok", 
"Second Mateq", 
"Boy/Cook", 
"Carp[enter", 
"Apprentice.", 
"First Officer[?]", 
"Third Mate/Clerk", 
"Fisrt Officer", 
"Rank", 
"Sail Ward", 
"Stweard", 
"Ist Mate", 
"Assistant[?]", 
"Servant", 
"ond mate", 
"? Mate", 
"Boston", 
"Mate?", 
"Assistance", 
"Third mate", 
"3rd officer", 
"Apprentice and Cook", 
"Greenhand & Carpenter", 
"Assistant & clerk", 
"3rd mate", 
"Carpenter & seaman", 
"Super cargo", 
"Cook & boy",           
"Not given.", 
"Apprentice to Captain", 
"Sailing Master", 
"Super cargo or consigne", 
"Apprentice and Boy", 
"1st mate?", 
"Green hand", 
"Sail-maker", 
"Joint supercargo", 
"Captain assistand", 
"Factor", 
"Apprentice seaman", 
"Steward[?]", 
"Seaman/Boy", 
"1 officer",
"2 officer",
"Ordinary? Seaman", 
"Seaman & carpenter", 
"Chief mate", 
"Cool", 
"Stacker",
"Seaman-Cook",
"Seaman and Cooper",
"Seaman/Steward",
"Steward?", 
"Cook?", 
"Super cargp", 
"1st maste", 
"Seaman Ordy",
"Ordinary seamab",
"1sr mate",
"Seamna",
"Duxbury",
"Cabin passenger", 
"Ordinary, Seaman", 
"Cooper and Seaman", 
"Supercargo[?]",
"3rd Mate/Clerk"),

Position3 = c("Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Cook",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Cook",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Unknown",
"Steward",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Orderly",
"Mate (1st, 2nd, 3rd)",
"Pilot/Steerer",
"Ship Keeper",
"Steward",
"Sailmaker",
"Seaman",
"Orderly",
"Cabin Boy",
"Orderly",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Harpoonsman",
"Cooper",
"Carpenter",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Carpenter",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Clerk",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Carpenter",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Armorer",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Boatswain",
"Seaman",
"Supercargo",
"Captain/Master",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Steward",
"Passenger",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Unknown",
"Cook",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Gunner",
"Clerk",
"Seaman",
"Passenger",
"Carpenter",
"Carpenter",
"Seaman",
"Captain/Master",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Seaman",
"Supercargo",
"Purser",
"Unknown",
"Servant/Assistant",
"Apprentice",
"Seaman",
"Seaman",
"Cook",
"Servant/Assistant",
"Mate (1st, 2nd, 3rd)",
"Clerk",
"Unknown",
"Clerk",
"Seaman",
"Gunner",
"Fifer",
"Seaman",
"Seaman",
"Drummer",
"Mate (1st, 2nd, 3rd)",
"Cabin Boy",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Cooper",
"Apprentice",
"Clerk",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Sailmaker",
"Seaman",
"Captain/Master",
"Pilot/Steerer",
"Supercargo",
"Sailmaker",
"Cook",
"Mate (1st, 2nd, 3rd)",
"Cook",
"Carpenter",
"Apprentice",
"Officer (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Sail Ward",
"Steward",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant",
"Servant/Assistant",
"Mate (1st, 2nd, 3rd)",
"Mate (1st, 2nd, 3rd)",
"Unknown",
"Mate (1st, 2nd, 3rd)",
"Servant/Assistant",
"Mate (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Cook",
"Carpenter",
"Clerk",
"Mate (1st, 2nd, 3rd)",
"Carpenter",
"Supercargo",
"Cook",
"Unknown",
"Apprentice",
"Sailing Master",
"Supercargo",
"Apprentice",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Sailmaker",
"Supercargo",
"Servant/Assistant",
"Factor",
"Apprentice",
"Steward",
"Seaman",
"Officer (1st, 2nd, 3rd)",
"Officer (1st, 2nd, 3rd)",
"Seaman",
"Carpenter",
"Mate (1st, 2nd, 3rd)",
"Cook",
"Seaman",
"Cook",
"Cooper",
"Steward",
"Steward",
"Cook",
"Supercargo",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Seaman",
"Mate (1st, 2nd, 3rd)",
"Seaman",
"Unknown",
"Passenger",
"Seaman",
"Cooper",
"Supercargo",
"Mate (1st, 2nd, 3rd)"))
```

```{r, echo = FALSE, include=FALSE}
salem_data_tidy_complexion2_position3_year_1797_1832 <- salem_data_tidy_complexion2_year_1797_1832 %>% 
  left_join(Position3, by = "Position")
```

```{r, echo = FALSE}
salem_data_tidy_complexion2_position3_year_1797_1832 %>% 
  filter(Position3 == "Cook") %>% 
ggplot(aes(x = Complexion2)) +
  geom_bar() + coord_flip() + labs(title = "Fig.5 Ship Cooks Departing Salem, 1797-1832", x = "Complexion", y = "Total", caption = "'Stewards' are removed and just cooks remain, but not much as changed from Fig.4")
```

```{r}
write.csv(salem_data_tidy_complexion2_position3_year_1797_1832, file = "salem data - joined with tidy complex,pos,year 1797-1832.csv")
```


```{r, echo = FALSE, include=FALSE}

salem_data_world_connections_year_1797_1832 <- salem_data_tidy_complexion2_position3_year_1797_1832 %>% 
  filter(Complexion2 == "Brown/Mulatto" | Complexion2 == "Indian" | Complexion2 == "Yellow/Olive")
```

```{r, echo = FALSE, include=FALSE}

BirthPlace2 <- data_frame(
  BirthPlace = c("Manchester",
"Maryland",
"Portsmouth, NH?",
"Java?",
"Petersbury",
"Delaware",
"Ipswich",
"Portsmouth",
"Baltimore",
"Boston",
"New York",
"Philadelphia",
"Germantown",
"Orleans, Cape Cod",
"Stockholm",
"Africa",
"Nantucket",
"New Orleans",
"Salem",
"Bridgeport",
"Canton",
"USA",
"Alexandria",
"Georgetown",
"Marblehead",
"Newton, NJ",
"Bath",
"North Kingston",
"Dunbarton, NH",
"Mississippi",
"Providence, R.I.",
"Rhode Island",
"Gloucester",
"Portland",
"Norwalk",
"Island of Tucina?",
"Newton",
"Kemacton?",
"Hingham",
"Beverly",
"Charleston",
"Kington, Pennsylvania",
"Gottenburg?",
"Albany",
"Massachusetts",
"Hampshire",
"Danzig",
"Norfolk",
"Danvers",
"England",
"Newport, RI",
"New Bern, NC",
"Lime Lyme?",
"St. Martin",
"South Carolina",
"Andover",
"New Jersey",
"Newark, (NJ)",
"Calcutta",
"?",
"Portugal",
"Helsingford",
"Altona",
"Newport, (RI)",
"Bengal",
"Wallingford",
"Worcester",
"Charles County",
"China",
"Sardinia",
"St. Iago",
"Cattaro",
"Prince George Virginia",
"Williamstown",
"Buck's County",
"St. Domingo",
"Oporto",
"Wilmington",
"Hide County, N.L.?",
"Norway",
"Island of Magdaline",
"Granby",
"New Bedford",
"Annapolis",
"Charles County, MD",
"Edenton",
"Cape Verde",
"Rio Janeiro",
"India",
"Newburyport",
"Hopkinton",
"Copenhagen",
"Virginia",
"Bucks County, PA",
"S. America",
"Litchfield, CT",
"Madeira",
"Sweden",
"Helsinburgh",
"Savannah",
"Montgomery",
"Gottenburg",
"Beaufort, SC",
"Kent?",
"Mt. Desert",
"Camden",
"Peru, NY",
"Stetten",
"Charlestown",
"Deer Isle",
"Stettin",
"Narragansett, RI",
"Mawee",
"Connecticut",
"North Bergen",
"Richmond",
"Rio de Janeiro",
"Richmond, VA",
"Southwark?",
"Bucks County",
"Manilla",
"Dram, Norway",
"Newport",
"Holstein",
"Pennsylvania",
"Georgetown, MD",
"Charlestown, SC",
"Albany, NY",
"Essex County",
"Somersett Conty",
"Topsfield",
"Trieste",
"Elson fort",
"Westchester Co.",
"Newark, N. J.",
"Leghorn",
"Little York",
"Falmar, Sweden",
"Long Island",
"East India",
"Kennebrook",
"Martha Vine Yard",
"Norfolk Va",
"Somerset",
"Accomack",
"Isle of Magdalena",
"Fells Point, MD",
"Calmar",
"Berwick",
"Topsieild",
"State of New York",
"Marthas Vinyard",
"Cumberland County, NJ",
"Cumberland",
"Middleton",
"Southampton",
"Italy",
"Posquotark",
"NewBern",
"Hamburg",
"Masschusetts",
"Duxbury",
"Snowhill",
"Wiscasset",
"East Indies",
"Sumatra"),

City = c("Manchester",
"NA",
"Portsmouth",
"NA",
"Petersburg",
"NA",
"Ipswich",
"Portsmouth",
"Baltimore",
"Boston",
"New York",
"Philadelphia",
"Germantown",
"Orleans, Cape Cod",
"Stockholm",
"NA",
"Nantucket",
"New Orleans",
"Salem",
"Bridgeport",
"Canton",
"NA",
"Alexandria",
"Georgetown",
"Marblehead",
"Newtown",
"Bath",
"Kingston",
"Dunbarton",
"NA",
"Providence",
"NA",
"Gloucester",
"Portland",
"Norwalk",
"NA",
"Newton",
"Thomaston",
"Hingham",
"Beverly",
"Charleston",
"Kingston",
"Gothenburg",
"Albany",
"NA",
"Hampshire",
"Danzig",
"Norfolk",
"Danvers",
"NA",
"Newport",
"New Bern",
"Lyme",
"NA",
"NA",
"Andover",
"NA",
"Newark",
"Calcutta",
"NA",
"NA",
"Helsinki",
"Altona",
"Newport",
"Bengal",
"Wallingford",
"Worcester",
"Charles County",
"NA",
"NA",
"St. Iago",
"Kotor",
"Prince George",
"Williamstown",
"Buck's County",
"NA",
"Porto",
"Wilmington",
"Hide County",
"NA",
"Maddalena",
"Granby",
"New Bedford",
"Annapolis",
"Charles County",
"Edenton",
"NA",
"Rio de Janeiro",
"NA",
"Newburyport",
"Hopkinton",
"Copenhagen",
"NA",
"Buck's County",
"NA",
"Litchfield",
"NA",
"NA",
"Helsinki",
"Savannah",
"Montgomery",
"Gothenburg",
"Beaufort",
"Kent County",
"Mt. Desert",
"Camden",
"Peru",
"Stetten",
"Charlestown",
"Deer Isle",
"Szczecin",
"Narragansett",
"NA",
"NA",
"North Bergen",
"Richmond",
"Rio de Janeiro",
"Richmond",
"Southwick",
"Buck's County",
"Manila",
"Dram",
"Newport",
"Holstein",
"NA",
"Georgetown",
"Charleston",
"Albany",
"Essex County",
"Somerset County",
"Topsfield",
"Trieste",
"Elson Fort",
"Westchester",
"Newark",
"Livorno",
"Little York",
"Falmar",
"Long Island",
"East India",
"Kennebunk",
"Martha's Vineyard",
"Norfolk",
"Somerset County",
"Accomack",
"Maddalena",
"Fells Point",
"Kalmar",
"Berwick",
"Topsfield",
"NA",
"Martha's Vineyard",
"Cumberland County",
"Cumberland",
"Middleton",
"Southampton",
"NA",
"Pasquotank",
"New Bern",
"Hamburg",
"NA",
"Duxbury",
"Snowhill",
"Wiscasset",
"NA",
"NA"),

State = c("Massachusetts",
"Maryland",
"New Hampshire",
"NA",
"Virginia",
"Delaware",
"Massachusetts",
"New Hampshire",
"Maryland",
"Massachusetts",
"New York",
"Pennsylvania",
"Maryland",
"Massachusetts",
"NA",
"NA",
"Massachusetts",
"Louisiana", 
"Massachusetts",
"Connecticut",
"NA",
"NA",
"Virginia",
"Maryland",
"Massachusetts",
"New Jersey",
"Maine",
"NA",
"New Hampshire",
"Mississippi",
"Rhode Island",
"Rhode Island",
"Massachusetts",
"Maine",
"Connecticut",
"NA",
"Massachusetts",
"Connecticut",
"Massachusetts",
"Massachusetts",
"South Carolina",
"Pennsylvania",
"NA",
"New York",
"Massachusetts",
"Massachusetts",
"NA",
"Virginia",
"Massachusetts",
"NA",
"Rhode Island",
"North Carolina",
"Connecticut",
"NA",
"South Carolina",
"Massachusetts",
"New Jersey",
"New Jersey",
"NA",
"NA",
"NA",
"NA",
"NA",
"Rhode Island",
"NA",
"Connecticut",
"Massachusetts",
"Maryland",
"NA",
"NA",
"NA",
"NA",
"Virginia",
"Massachusetts",
"Pennsylvania",
"NA",
"NA",
"Delaware",
"North Carolina",
"NA",
"NA",
"Connecticut",
"Massachusetts",
"Maryland",
"Maryland",
"North Carolina",
"NA",
"NA",
"NA",
"Massachusetts",
"Massachusetts",
"NA",
"Virginia",
"Pennsylvania",
"NA",
"Connecticut",
"NA",
"NA",
"NA",
"Georgia",
"Alabama",
"NA",
"South Carolina",
"Maryland",
"Maine",
"New Jersey",
"New York",
"NA",
"Massachusetts",
"Maine",
"NA",
"Rhode Island",
"NA",
"Connecticut",
"New Jersey",
"Virginia",
"NA",
"Virginia",
"Massachusetts",
"Pennsylvania",
"NA",
"NA",
"Rhode Island",
"NA",
"Pennsylvania",
"Maryland",
"South Carolina",
"New York",
"Massachusetts",
"Maryland",
"Massachusetts",
"NA",
"NA",
"New York",
"New Jersey",
"NA",
"Pennsylvania",
"NA",
"New York",
"NA",
"Maine",
"Massachusetts",
"Virginia",
"Maryland",
"Virginia",
"NA",
"Maryland",
"NA",
"Pennsylvania",
"Massachusetts",
"New York",
"Massachusetts",
"New Jersey",
"Maryland",
"Massachusetts",
"Massachusetts",
"NA",
"North Carolina",
"North Carolina",
"NA",
"Massachusetts",
"Massachusetts",
"Maryland",
"Maine",
"NA",
"NA"),

Country = c("USA",
"USA",
"USA",
"Java",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Sweden",
"Africa",
"USA",
"USA",
"USA",
"USA",
"China",
"NA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Jamaica",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Island of Terceira",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Sweden",
"USA",
"USA",
"USA",
"Prussia",
"USA",
"USA",
"England",
"USA",
"USA",
"USA",
"St. Martin",
"USA",
"USA",
"USA",
"USA",
"India",
"NA",
"Portugal",
"Sweden",
"Denmark",
"USA",
"India",
"USA",
"USA",
"USA",
"China",
"Sardinia",
"Cuba",
"Montenegro",
"USA",
"USA",
"USA",
"St. Domingo",
"Portugal",
"USA",
"USA",
"Norway",
"Sardinia",
"USA",
"USA",
"USA",
"USA",
"USA",
"Cape Verde",
"Brazil",
"India",
"USA",
"USA",
"Denmark",
"USA",
"USA",
"NA",
"USA",
"Madeira",
"Sweden",
"Sweden",
"USA",
"USA",
"Sweden",
"USA",
"USA",
"USA",
"USA",
"USA",
"Prussia",
"USA",
"USA",
"Prussia",
"USA",
"Maui",
"USA",
"USA",
"USA",
"Brazil",
"USA",
"USA",
"USA",
"Philippines",
"Norway",
"USA",
"Denmark",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Italy",
"Sweden",
"USA",
"USA",
"Italy",
"USA",
"Sweden",
"USA",
"India",
"USA",
"USA",
"USA",
"USA",
"USA",
"Sardinia",
"USA",
"Sweden",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"USA",
"Italy",
"USA",
"USA",
"Germany",
"USA",
"USA",
"USA",
"USA",
"East Indies",
"Sumatra"),

Region = c("North America",
"North America",
"North America",
"East Indies",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Scandanavia",
"Africa",
"North America",
"North America",
"North America",
"North America",
"North America",
"NA",
"North America",
"North America",
"North America",
"North America",
"North America",
"Caribbean",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Atlantic Islands",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Scandanavia",
"North America",
"North America",
"North America",
"Europe",
"North America",
"North America",
"Europe",
"North America",
"North America",
"North America",
"Caribbean",
"North America",
"North America",
"North America",
"North America",
"India",
"NA",
"Europe",
"Scandanavia",
"Europe",
"North America",
"India",
"North America",
"North America",
"North America",
"Asia",
"Europe",
"Caribbean",
"Europe",
"North America",
"North America",
"North America",
"Caribbean",
"Europe",
"North America",
"North America",
"Scandanavia",
"Europe",
"North America",
"North America",
"North America",
"North America",
"North America",
"Africa",
"South America",
"India",
"North America",
"North America",
"Europe",
"North America",
"North America",
"South America",
"North America",
"Atlantic Islands",
"Scandanavia",
"Scandanavia",
"North America",
"North America",
"Scandanavia",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"North America",
"North America",
"Europe",
"North America",
"Pacific Islands",
"North America",
"North America",
"North America",
"South America",
"North America",
"North America",
"North America",
"Asia",
"Scandanavia",
"North America",
"Europe",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"Scandanavia",
"North America",
"North America",
"Europe",
"North America",
"Scandanavia",
"North America",
"India",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"North America",
"Scandanavia",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"Europe",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"North America",
"India",
"India"))
```


```{r, echo = FALSE, include=FALSE}
salem_data_world_connections_BirthPlace2_year_1797_1832 <- salem_data_world_connections_year_1797_1832 %>% 
  left_join(BirthPlace2, by = "BirthPlace")
```

```{r, echo=FALSE}
salem_data_tidy_complexion2_position2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Position2 != "Unknown") %>% 
  ggplot(aes(x = Position2)) + geom_bar() + facet_wrap(~ Complexion2, scales = "free_x") +coord_flip() + labs(title = "Fig.6 Global Sailors, 1797-1832", x = "Position", y = "Total", subtitle = "Craftsman = Sailmaker, Carpenter, Cooper, Harpoonsman", caption = "Side-by-Side Proportional Occupation by Complexion")
```


```{r, echo = FALSE}
salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Position3 == "Cook", Country != "USA", Country != "NA") %>% 
  ggplot(aes(x = Country, fill = City))+
  geom_bar() + labs(title = "Fig.7 Global Cooks, 1797-1832", y = "Total", subtitle = "Cooks born in the USA have been filtered out (around 40)")
```

Here one can get a sense of these individuals' birthplaces.



```{r, echo=FALSE}

salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Country != "USA", Country != "NA") %>% 
  ggplot(aes(x = Country, fill = Position3)) + geom_bar() +coord_flip() + labs(title = "Fig.9 Global Sailors; Range of Diversity, 1797-1832", x = "Country of Birth", y = "Total", fill = "Position")

```

We can also discover what foreign cities were represented aboard Salem ships. 

```{r, echo=FALSE}
salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Country != "USA", Country != "NA", Region == "Europe"| Region == "Atlantic Islands" | Region == "Scandanavia", City != "NA") %>% 
  ggplot(aes(x = City, fill = Position3)) + geom_bar() +coord_flip() + labs(title = "Fig.10 European and Scandanavian Cities", x = "City of Birth", y = "Total Sailors Born Here", fill = "Position")
```

```{r, echo=FALSE}

salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Country != "USA", Country != "NA", Region == "Asia"| Region == "Pacific Islands" | Region == "India", City != "NA") %>% 
  ggplot(aes(x = City, fill = Position3)) + geom_bar() +coord_flip() + labs(title = "Fig.11 Far East Cities", x = "City of Birth", y = "Total Sailors Born Here", fill = "Position")
```

```{r, echo=FALSE}

salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Complexion2 != "Unknown", Country != "USA", Country != "NA", Region == "Caribbean" | Region == "South America", City != "NA") %>% 
  ggplot(aes(x = City, fill = Position3)) + geom_bar() +coord_flip() + labs(title = "Fig.12 South American and Caribbean Cities", x = "City of Birth", y = "Total Sailors Born Here", fill = "Position")

```

It is evident that sailors departing Salem included a range of individuals from around the world. This presents a more complicated and diverse picture of the traditional small-town New England sailor.

```{r}

salem_data_world_connections_BirthPlace2_year_1797_1832 %>% 
  filter(Complexion == "Black/Dark")
```

